\documentclass[12pt]{beamer}
\usepackage{url,amsmath,bm,graphicx,listings}
\usetheme{default}
\title[NYC Restaurant Inspections]{NYC Restaurant Inspections}
\subtitle{Analysis and $k$-Means Clustering}
\author{Andrew Kaluzny}
\date{November 2, 2014}


\begin{document}
\maketitle

\begin{frame}{Sources}
\begin{itemize}
	\item MacQueen, J. (1967) ``Some Methods for Classification and 
		Analysis of Multivariate Observations.'' In \emph{Proceedings of 
		the Fifth Berkeley Symposium on Mathematical Statistics and Probability},
		eds L. M. Le Cam and J. Neyman. Berkeley, CA: University of California Press.
		
	\item (2014) ``Determining the number of clusters in a data set.'' Wikipedia.
		Wikimedia Foundation, Inc. 
		\url{http://en.wikipedia.org/wiki/Determining_the_number_of_clusters_in_a_data_set}
		
	\item R Core Team. (2014) ``R: A Language and Environment for Statistical Computing.''
		R Foundation for Statistical Computing. Vienna, Austria.
		\url{http://www.R-project.org}
\end{itemize}
\end{frame}

\begin{frame}{Sources: Data}
\begin{itemize}
	\item (2014) ``DOHMH New York City Restaurant Inspection Results.''
		NYC Open Data. New York, NY: The City of New York.
		\url{https://data.cityofnewyork.us/Health/DOHMH-New-York-City-Restaurant-Inspection-Results/xx67-kt59}
	
	\item (2012) ``How We Score and Grade.'' New York City Department of Health and
		Mental Hygiene. New York, NY: The City of New York.
		\url{http://www.nyc.gov/html/doh/downloads/pdf/rii/how-we-score-grade.pdf}
		
	\item (2010) ``Self-Inspection Worksheet for Food Service Establishments.''
		Bureau of Food Safety and Community Sanitation. New York, NY: The City of 
		New York.
		\url{http://www.nyc.gov/html/doh/downloads/pdf/rii/self-inspection-worksheet.pdf}
\end{itemize}
\end{frame}

\section{Background}
\begin{frame}{Restaurant Inspections}
\begin{itemize}
	\vfill
	\item Began July 2010
	\vfill
	\item Itemized violations contribute to a score based on severity
	\begin{itemize}
		\item 2B: Hot food not held at or above $140^{\circ}$F, 7 to 28 points
		\item 10J: ``Wash Hands'' sign not posted at hand-wash facility, 2 points
		\item etc. 
	\end{itemize}
	\vfill
	\item A: 0--13, B: 14--27, C: 28 and higher
	\vfill
	\item Not all inspections are graded, low grades lead to re-inspection
	\vfill
\end{itemize}
\end{frame}

\section{Getting the Data}
\begin{frame}{Getting and Cleaning the Data}
\begin{itemize}
	\vfill
	\item Data set available through NYC Open Data
	\vfill
	\item Data needs to be cleaned
	\begin{itemize}
		\item e.g. \texttt{Fontana"s} $\rightarrow$ \texttt{Fontana's}
	\end{itemize}
	\vfill
	\item Data needs to be parsed
	\vfill
	\item Code performance concerns
	\begin{itemize}
		\item $\approx24,500$ rows of data
		\item R quirks
	\end{itemize}
	\vfill
\end{itemize}
\end{frame}

\section{Preliminary Results}
\begin{frame}{Preliminary Analysis}
Stats about things
So many things!
\end{frame}

\begin{frame}{More Analysis}
Probably more stuff will be here!
\end{frame}

\section{k-Means Clustering}
\begin{frame}{Clustering}
\vfill
Why do we cluster things?
\begin{itemize}
	\item Exploratory analysis
	\item Classification
\end{itemize}
\vfill
$k$-Means clustering
\begin{itemize}
	\item Clusters defined by their means
	\item Originated as an information theory problem (S.~P.~Lloyd,~1957)
	\item Analogy to the case of estimating a single mean
\end{itemize}
\vfill
\end{frame}

\begin{frame}{$k$-Means Clustering}
Definitions!
Weaknesses?
\end{frame}

\begin{frame}{Convergence of $k$-Means}
Theorem!

Proof (outline, at least)
\end{frame}

\begin{frame}{Pathological Distributions}
\begin{itemize}
	\vfill
	\item Circle
	\vfill
	\item Square
	\vfill
	\item Rectangle
	\vfill
\end{itemize}
\end{frame}

\begin{frame}{What do we want to cluster?}
Markov chains!
Specific violations!
\end{frame}

\begin{frame}{Finding $k$}
\vfill
$k$ is a free parameter--how do we find it?
\begin{itemize}
	\item Increasing $k$ will always reduce sum-of-squares
\end{itemize}
\vfill
The elbow method
\begin{itemize}
	\item Find where increasing $k$ has less of an impact (the ``elbow'')
\end{itemize}
\vfill
\end{frame}

\section{Clustering Results}
\begin{frame}{Clustering Results}
Clustering results!
(Probably several slides)
\end{frame}

\section{Conclusions}
\begin{frame}{Conclusion}
Conclusions!
\end{frame}

\end{document}